Evolution of solar wind discontinuities in the inner heliosphere

### 2024-02-08 index.qmd
update
remove freeze
update websites

---
title: Evolution of solar wind discontinuities in the inner heliosphere
subtitle: PSP and Earth conjunctions and alignments
author:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
    roles: writing
    corresponding: true
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
  - name: Shi Chen
    orcid: 0000-0002-2582-7085
    affiliation: University of California, Los Angeles
code-links:
  - repo
  - href: https://app.tana.inc?nodeid=PZ6j7iriic2l
    text: Tana
  - href: zotero://select/library/collections/L9JC7XAI
    text: Zotero
---

@@

@@

![](images/paste-19.png)

>>>>

---
title: Evolution of solar wind discontinuities in the inner heliosphere
subtitle: PSP and Earth conjunctions and alignments
author:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
    roles: writing
    corresponding: true
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
code-links:
  - repo
  - href: https://app.tana.inc?nodeid=PZ6j7iriic2l
    text: Tana
  - href: zotero://select/library/collections/L9JC7XAI
    text: Zotero
---

@@

## 02/08/2024

![](./figures/density_distribution){#fig-distribution}

![](./figures/thickness_current){#fig-thickness-current}

::: {.column-page}
{{< embed notebooks/10_results.ipynb#fig-dn-db >}}

{{< embed notebooks/10_results.ipynb#fig-dv >}}
:::

##

![](images/paste-20.png)

@@

![PSP Observation Overvall](images/paste-19.png)
